MaxEnt: What is it good for?

### 2015-06-19 ms.tex
Abstract edits

\abstract{I discuss the principle of maximum (relative) entropy as a tool
for updating probability distributions. This principle is intuitively
compelling, as I will show through examples. However, it has been neglected
by most modern practitioners of Bayesian inference. I will argue that there
are two main reasons for this: i) some questionable applications
and discussions of the principle have appeared in the literature, and
ii) the situation which the principle seems designed to handle never seems
to arise in practical applications.}

>>>>

\abstract{I discuss the principle of maximum (relative) entropy as a tool
for updating probability distributions. This principle is intuitively
compelling, as I will show through examples. However, it has been neglected
by most modern practitioners of Bayesian inference. There
are two main reasons for this: i) some questionable applications
and discussions of the principle have appeared in the literature, and
ii) the situation which the principle seems designed to handle never seems
to actually arise in practical applications. I will attempt to define the
situations in which MaxEnt could be practically useful.}
